%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
% ---- in your preamble ------------------------------------
\newcommand{\skillsep}{\hspace{0.6em}\textbar\hspace{0.6em}}
% ----------------------------------------------------------

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Akshat Sharma} \\ \vspace{6pt}
    \small 519-992-7451$|$ \href{mailto:akshat@akshatsharma.ca}{\underline{akshat@akshatsharma.ca}} $|$ 
    \href{https://www.linkedin.com/in/akshat8d/}{\underline{LinkedIn}} $|$
    \href{https://github.com/Cyoger}{\underline{GitHub}} $|$
    \href{https://akshatsharma.ca}{\underline{akshatsharma.ca}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Software Developer}{Apr 2024 -- Present}
  {\href{https://tessonics.com/}{\textbf{Tessonics}}}{Windsor, ON}
  \resumeItemListStart
    \resumeItem{Built a \textbf{C++} PLC simulator that mirrors real production traffic, accelerating integration tests for the \textbf{RIWA} platform.}
    \resumeItem{Engineered a real-time Hall-effect current-detection algorithm in \textbf{C++}, achieving $<$\!10 ms end-to-end latency.}
    \resumeItem{Authored backward-compatible 32-bit \textbf{C++} DLLs that exposes a drop-in API, bridging legacy software to a modern \textbf{C++} inference server via WebSocket and delivering real-time deep-learning predictions with no code rewrites.}
    \resumeItem{Built a \textbf{Python}-based \textbf{Debian} packaging pipeline and a self-hosted \textbf{GitHub Actions} runner, fully automating CI/CD and release distribution for the monorepo.}
    \resumeItem{Designed an \textbf{ImGui} GUI for effortless JSON configuration, cutting technician setup time and reducing deployment errors across customer sites.}
    \resumeItem{Automated cleaning, analysis, and visualization of \textbf{EEG} \& Hypnogram time-series data using \textbf{NumPy} and \textbf{matplotlib}.}
    \resumeItem{Developed STM32 firmware (\textbf{C}) that integrates the \textbf{MCP4725} DAC and \textbf{RX8900} RTC for the SONYA sleep wearable.}
    \resumeItem{Implemented a \textbf{Bluetooth Low Energy (BLE)} GATT service on the STM32 that lets users remotely adjust stimulation intensity and toggle operating modes on the sleep-wearable in real time.}
    \resumeItem{Optimized \textbf{ISM330DHCX} IMU data capture via FIFO and I\textsuperscript{2}C, ensuring synchronized, real-time motion streams for onboard processing.}
\resumeItemListEnd

  \resumeSubheading
    {Undergraduate Research Assistant}{Jan 2023 -- Apr 2024}
    {\href{https://www.uwindsor.ca/idir/}{\textbf{Institute of Diagnostic Imaging Research}}}{Windsor, ON}
    \resumeItemListStart
      \resumeItem{Conducted interdisciplinary research in deep learning (AutoEncoders, GANs, U-Nets) for creation of Synthetic Welds using Generative Models for Non-Destructive Ultrasound Evaluation.}
      \resumeItem{Collaborated on deep learning model development in \textbf{TensorFlow}; curated datasets, and developed Python scripts (using \textbf{OpenCV}, \textbf{NumPy}, \textbf{matplotlib}) for ultrasound image analysis in resistance spot weld evaluation.}

    \resumeItemListEnd

  \resumeSubHeadingListEnd


  %
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}

\begin{itemize}[leftmargin=10pt, itemsep=0.5pt, label={}]
  \small
  \item \textbf{Languages:}\enspace
        C\skillsep
        C++17\skillsep
        C++20\skillsep
        Python\skillsep
        Java\skillsep
        Kotlin\skillsep
        Go\skillsep
        C\#\skillsep
        SQL

  \item \textbf{ML \& Vision:}\enspace
        TensorFlow\skillsep
        PyTorch\skillsep
        Keras\skillsep
        OpenCV\skillsep
        NumPy\skillsep
        SciKit-Learn\skillsep
        matplotlib

  \item \textbf{DevOps:}\enspace
        Git\skillsep
        Docker\skillsep
        GitHub Actions\skillsep
        CMake\skillsep
        Conan\skillsep

  \item \textbf{Database:}\enspace
        PostgreSQL\skillsep
        SQLite\skillsep
        MySQL\skillsep
        Redis

  \item \textbf{Embedded / HW:}\enspace
        STM32CubeIDE\skillsep
        FreeRTOS\skillsep
        I\textsuperscript{2}C\skillsep
        SPI\skillsep
        Arduino
\end{itemize}


% -----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\href{https://github.com/Cyoger/CIFAR-100-Deep-learning-analysis}{\textbf{CIFAR-100 Analysis}} $|$ \emph{Python, TensorFlow, Keras, NumPy}}{Nov 2023 - Dec 2023}
          \resumeItemListStart
            \resumeItem{Developed a comprehensive deep learning pipeline for CIFAR-100 dataset, achieving 80\% accuracy with CNNs and 85\% with ResNet-50.}
            \resumeItem{Implemented data augmentation techniques to enhance model robustness and prevent overfitting.}
          \resumeItemListEnd
  \resumeSubHeadingListEnd 

  %-----------EDUCATION-----------
  \section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Windsor}{Jan 2021 -- Apr 2024}
      {Bachelor of Computer Science Honours}{Windsor, ON}
    \resumeItemListStart
      \resumeItem{\textit{Specialization in Artificial Intelligence, Minor in Mathematics}}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd  

%-----------VOLUNTEER AND AWARDS-----------
\section{Volunteer \& Awards}
\resumeItemListStart
  \resumeItem{\textbf{Event Coordinator, Computer Science Society} \hfill 2023 -- 2024\\
              Organized events that served 100+ students each term and streamlined logistics to improve attendee experience.}
  \resumeItem{\textbf{Dean's Honour Roll} \hfill 2021 -- 2024\\
              University of Windsor}
\resumeItemListEnd

%-------------------------------------------
\end{document}
